% Robotics Institute Technical Report
%
% Unofficial Template for RI Technical Reports
% Use with latex2e
%
% Modified by: David Fouhey, Oct 2014
% Created by: Daniel Morris, Dec 2000
%
% DM:
%   Since I was unable to find a template for Technical Reports, I made up my
%   own.  Use it at your own risk -- as I am not a latex guru.


\documentclass[twoside,10pt]{report}
\usepackage{marginnote}
\usepackage[left=1.5in,right=1.5in,top=1.5in,bottom=1.5in]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{graphicx,amsmath,amssymb,multirow,booktabs,color,verbatim,cite,placeins}
\usepackage{algorithm, algpseudocode}
\usepackage[font=scriptsize]{subcaption}
\usepackage[font=scriptsize]{subfig}
\usepackage{layouts,array,wrapfig}
\usepackage[normalem]{ulem}
\usepackage{tgpagella}
\usepackage{hyperref}
\usepackage{url}
\usepackage{appendix}
\newcommand*{\QEDB}{\hfill\ensuremath{\square}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%DF: This needs to be removed to get 
%rid of all watermarks
%\usepackage{draftwatermark}
%\SetWatermarkText{DRAFT}
%\SetWatermarkScale{0.5}
%\SetWatermarkLightness{0.90}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%DF: Nuke all the notes by using 
%the second note definition below
%\newcommand{\note}[1]{\textcolor{red}{#1}}
\newcommand{\note}[1]{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Hyperlink setup
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


%I usually like to put more figures on a page with text than latex's
%default
\renewcommand{\textfraction}{0.05}
\renewcommand{\topfraction}{0.9}
\renewcommand{\floatpagefraction}{0.8}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}


\newcommand{\clearemptydoublepage}{\newpage{\pagestyle{empty}\cleardoublepage}}
\newcommand*\NewPage{\newpage\null\thispagestyle{empty}\newpage}

%Table of contents stuff
\setcounter{tocdepth}{1}

\begin{document}

% Adding notations
\input{notation.tex}

%title page
\input{titlepage.tex}
\clearpage

\NewPage

\vspace*{4cm}
\begin{center}
  \textit{For my brother, who put the fear of mediocrity in me.} \\
  \textit{For my mom, for all her sacrifices to help me pursue my dreams.}
\end{center}

%start the forematter 
\pagenumbering{Roman}

\setcounter{page}{1}
\NewPage
\begin{centering} \section*{Abstract} \end{centering}
\input{abstract.tex}

\NewPage

\begin{centering} \section*{Acknowledgements} \end{centering}
\input{acknowledgements.tex}

\NewPage


\tableofcontents
\clearpage

\NewPage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Include in final thesis
\clearpage \listoffigures
\clearpage \listoftables
\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\NewPage

%start the actual document
\pagenumbering{arabic}
\setcounter{page}{1}


\chapter{Introduction}
\label{chap:introduction}
\input{introduction.tex}

\clearpage

\chapter{Navigation in Human Crowds : A Survey}
\label{chap:survey}
\input{survey.tex}

\clearpage

\chapter{Path Planning in Dynamic Environments with Adaptive Dimensionality}
\label{chap:ppad}
\input{ppad.tex}

\clearpage

\chapter{Modeling Cooperative Navigation in Dense Human Crowds}
\label{chap:oigp}
\input{oigp.tex}

\clearpage

%\chapter{Attention in Human Crowds}
%\label{chap:attn}
%\input{attn.tex}

%\clearpage

\chapter{Conclusion}
\label{chap:conclusion}
\input{conclusion.tex}


\clearpage

\appendix
\chapter{Code and Publications}
\label{chap:code-and-datasets}

\section{Code}
\label{sec:code}
\begin{itemize}
\item Code for the planning algorithm proposed in Chapter \ref{chap:ppad}, with dataset : \url{https://github.com/vvanirudh/sbpl_dynamic_adaptive_planner}
\item Code for the statistical model proposed in Chapter \ref{chap:oigp} : \url{https://github.com/vvanirudh/occupancy-IGP}
\end{itemize}

\section{Publications}
\label{sec:publications}

\begin{itemize}
\item The work presented in Chapter \ref{chap:ppad} was presented at SoCS 2016.
  \begin{quote}
    Vemula, Anirudh, Katharina Muelling, and Jean Oh. ``Path Planning in Dynamic Environments with Adaptive Dimensionality.'' In Ninth Annual Symposium on Combinatorial Search. 2016.
  \end{quote}
\item The work presented in Chapter \ref{chap:oigp} was presented at ICRA 2017.
  \begin{quote}
    Vemula, Anirudh, Katharina Muelling, and Jean Oh. ``Modeling Cooperative Navigation in Dense Human Crowds.'' In International Conference on Robotics and Automation. 2017.
  \end{quote}  
\end{itemize}

\chapter{Public Datasets}
\label{cha:public-datasets}

\begin{itemize}
\item ETH Dataset used for evaluation in Chapter \ref{chap:oigp} can be found here : \url{http://www.vision.ee.ethz.ch/en/datasets/}
\end{itemize}

%Include references using bst and bib files.
\bibliographystyle{finitplain}
%\bibliographystyle{apalike} 
{\small \bibliography{local}}


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
